---
title: "Lab 00 - Hello IDS!"
author: "Faaiz Mir"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("sophie", "beth", "beatrice", 
           "mohsin"),
  github_username = c("sophieghinculov", "bethpeters", "beashek1-spec", 
                      "mohsinabro06"), 
  colour = c("blue", "orange", "pink", 
             "orange"),
  hobby = c("tennis", "karate", "taekwondo", 
            "videogames"),
  favourite_number = c(8,2,6,7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows a collection of my team member's favorite colors, numbers, and GitHub usernames in one graph. 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favorite numbers from 1-10",
          title = "Introduction to my group")
```

labs() is used to changed the axes titles and other labels in the plot. 

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Perhaps a piechart would be more applicable in this case.